Mixture distribution data generation

### 2022-02-14 Ch3_samplesize/Datagen_viz.Rmd
Taking a different approach, so deleted previous lognormals that came from Ch2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=12, fig.height=6)
```

@@

```{r LoadFitData}
load("Ch2_distributions/Ch2_fits.RData")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=6, fig.height=4)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

@@
